Language-Based Security for Low-Level MPC

### 2024-09-10 csf25/ctj.tex
checkpoint

@@

\begin{fpfig}[t]{Syntax and Derivation Rules for $\minicat$ Confidentiality Types}{fig-cpj}
\small{
$$
\begin{array}{rcl@{\hspace{3mm}}l}
  t &::=& x \mid \cty{x}{T} \\
  \ty & \in & 2^{t} & \gdesc{types}\\
  \Gamma &::=& \varnothing \mid \Gamma; x : \ty & \gdesc{type environments}
\end{array} 
$$
\medskip
\begin{mathpar}
  \inferrule[DepTy]
  {}
  {\eqj{\varnothing}{\eqs}{\phi}{\vars(\phi)}}

  \inferrule[Encode]
  {\eqs \models \phi \eop \phi' \oplus \rx{w}{\cid} \\
   \oplus \in \{ \fplus,\fminus \}\\
   \eqj{R}{\eqs}{\phi'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{\phi}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
\end{mathpar}

\begin{mathpar}
  \inferrule[Send]
            {\eqj{R}{\eqs}{\phi}{\ty}}
            {\cpj{R}{\eqs}{x \eop \phi}{(x : \ty)}}

  \inferrule[Seq]
            {\cpj{R_1}{\eqs}{\phi_1}{\Gamma_1}\\
             \cpj{R_2}{\eqs}{\phi_2}{\Gamma_2}}
            {\cpj{R_1;R_2}{\eqs}{\phi_1 \wedge \phi_2}{\Gamma_1;\Gamma_2}}
\end{mathpar}
}
\end{fpfig}

\begin{fpfig}[t]{Dependencies in Corrupt Views: Derivation Rules}{fig-leakj}
\small{
\begin{mathpar}
  \inferrule
      {\cid \in C}
      {\leakj{\Gamma}{C}{\Gamma(\mx{w}{\cid})}}

  \inferrule
      {\leakj{\Gamma}{C}{T_1 \cup T_2}}
      {\leakj{\Gamma}{C}{T_1}}

  \inferrule
      {\leakj{\Gamma}{C}{\setit{ \mx{w}{\cid} }}}
      {\leakj{\Gamma}{C}{\Gamma(\mx{w}{\cid})}}

  \inferrule
      {\leakj{\Gamma}{C}{\setit{ \rx{w}{\cid} }} \\ \leakj{\Gamma}{C}{\setit{ \cty{\rx{w}{\cid}}{\ty} }} }
      {\leakj{\Gamma}{C}{\ty}}
\end{mathpar}
}
\end{fpfig}

>>>>

\cpjfig

@@

\subsection{Detecting Leakage Through Dependencies}

\leakjfig

Given a valid typing, we need to conservatively approximate the
information accessible by the adversary, who will have control over
all corrupt clients in $C$ given a partitioning $H,C$. In particular,
if the adversary has access to an encypted value and another value
that is dependent on its one-time-pad key-- i.e., access to values
with types of the forms:
$$
\setit{\cty{\rx{x}{\cid}}{\ty}} \qquad \setit{\rx{x}{\cid}, \ldots} 
$$
then we can conservatively assume that the adversary can decrypt the
value of type $\ty$.

### 2024-09-10 ppdp24/slides.tex
checkpoint

\begin{frame}{The Ideal Functionality}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item The \cemph{output} is made \emph{publicly available} by $\prog$
  \end{itemize}
  \cemph{The output may leak secret information to an adversary} trying to
  guess secret values.

@@

  \begin{exampleblock}{Example: 3-Party $\fplus$} %in $\mathbb{F}_2$ (where $\fplus$ is $\exor$ and $\ftimes$ is $\wedge$)}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \fplus\ \sx{2}{2}\ \fplus\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$.
  Therefore the adversary knows that either:
  $$
  \sx{1}{1} = 0 \text{\ and\ } \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \text{\ and\ } \sx{2}{2} = 0
  $$
  with equal joint probability of .5. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{itemize}
    \item The set of all protocol runs under all possible secrets and random tapes
      induces a probability distribution of program variables.
    \item Conditioning on the output and corrupt secrets =  declassification
      bounds.
    \item Conditioning on adversarial views tells us whether they leak information--
      if it changes the distribution of honest secrets.
  \end{itemize}

  \begin{alertblock}{Conditional Noninterference}
    The probability of honest secrets conditioned on the protocol output
    should not be changed by conditioning on adversarial views. 
  \end{alertblock}

  \begin{itemize}
  \item Sound for the standard \emph{passive simulator security} model.
  \item A \emph{hyperproperty} that accommodates traditional PL-based security
    mechanisms and theory. 
  \end{itemize}

>>>>

\begin{frame}{The Ideal Functionality}
  A \emph{protocol} $\prog$ implements an \emph{ideal functionality} $\idealf$,
  defined in terms of operations $(+,-,*)$ in a prime field $\mathbb{F}_p$.
  \begin{itemize}
  \item The inputs are \cemph{secret values} of \cemph{clients} in a \emph{federation}
    $\setit{1,...,j}$.
  \item The \cemph{output} is made \emph{publicly available} by $\prog$
  \end{itemize}
  \cemph{The output may leak secret information to an adversary} trying to
  guess secret values.

@@

  \begin{exampleblock}{Example: 3-Party $\fplus$ in $\mathbb{F}_2$ (where $\fplus$ is $\exor$ and $\ftimes$ is $\wedge$)}
  $$
  \idealf(\sx{1}{1},\sx{2}{2},\sx{3}{3}) =
  \sx{1}{1}\ \fplus\ \sx{2}{2}\ \fplus\ \sx{3}{3}
  $$
  Suppose in a run of $\prog$ the output of $\prog$ is 1 and $C = \{ 3 \}$ and
  the adversary knows $\sx{3}{3} = 0$.
  Therefore the adversary knows that either:
  $$
  \sx{1}{1} = 0 \text{\ and\ } \sx{2}{2} = 1
  $$
  or:
  $$
  \sx{1}{1} = 1 \text{\ and\ } \sx{2}{2} = 0
  $$
  with equal joint probability of .5. \cemph{Adversarial views from the run of $\prog$ should not
    allow the adversary better guesses.}
  \end{exampleblock}

@@

  \begin{itemize}
    \item The set of all protocol runs under all possible secrets and random tapes
      induces a probability distribution of program variables.
    \item Conditioning on the output and corrupt secrets =  declassification
      bounds.
    \item Conditioning on adversarial views = distribution of honest secrets.
  \end{itemize}

  \begin{alertblock}{Conditional Noninterference}
    The probability of honest secrets conditioned on the protocol output
    should not be changed by conditioning on adversarial views.

  \begin{itemize}
  \item Sound for the standard \emph{passive simulator security} model.
  %\item A \emph{hyperproperty} that accommodates traditional PL-based security
  %  mechanisms and theory. 
  \end{itemize}
  \end{alertblock}
